Verifying Demonstrations

### 2018-03-21 paper/DB-anon-cred.tex

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, although ideally this property should be desirable.

@@

    \(\rho_0\rgets \Z_q, \rho_1\rgets \Z_q\)
    &
    &
    \\

>>>>

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and an impersonating 
verifier (\ie public-key).
It will not protect against terrorist fraud, although ideally this property should be desirable.

@@

    \(\rho_0\rgets \ZZ_q, \rho_1\rgets \ZZ_q\)
    &
    &
    \\

### 2018-03-21 paper/SystemModel.tex

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
The strength function \(s\) can be used to regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.

>>>>

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in 
    \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t = \interval{t_s}{t_e}\subseteq \RR\) is a time interval and \(l = 
    N_\epsilon(x, y)\subseteq \RR^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}
The strength function \(s\) can be used to regulate trust in witnesses.
One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.

### 2018-03-21 paper/protocol.tex

\emph{Submission: \(\pi'\gets \PRIVOsubmit[cid, pid, wid, t_s, t_s', l, 
    wsig]\).}
\dots

>>>>

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
    wsig]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
correctness of \(pid\).
More specifically,
\begin{multline*}
  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
    \begin{aligned}
      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
    \end{aligned} \\
      (cid, pid, wid, t_s, t_s', l, wsig).
\end{multline*}
Finally, the participant uploads the tuple \[
  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
\] for permanent storage.

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][pid, wid, t_s, t_s', l, 
    wsig]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, 
  wsig]]\).
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{wid, wsig}\) as follows:
\begin{multline*}
  \pi_{wid, wsig}\gets \SPK\left\{ (sk_W) : \right. \\
    \begin{aligned}
      wid &= \ACprf[_{sk_W}][pid] \quad \land \\
      wsig &= \ACprf[_{sk_W}][wid, t_s, t_s', l] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{ssk}][sk_W]] \right\}
    \end{aligned} \\
      (pid, wid, t_s, t_s', l, wsig).
\end{multline*}
Finally, the witness uploads the tuple \[
  (pid, wid, t_s, t_s', t_e', l, wsig, \pi_{wid, wsig})
\] for permanent storage.
